Hemispheric Lateralization in ICH

### 2023-05-17 code/dataAnalysis/02analysis.qmd
mrs figures done

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Analysis"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
---

@@

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2

@@

@@

theme_set(theme_minimal(base_size = 10, base_family = "Figtree"))

@@

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = percentPatientsLabel),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = "Patients (%)",
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_fill_manual(values = myColors) +
  theme(
    plot.title = element_text(face = "bold", size = 100, lineheight = 0.1),
    plot.subtitle = element_text(size = 72, lineheight = 0.1),
    plot.caption = element_text(size = 22),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 20),
    legend.margin = margin(r = 75),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5),
    axis.title.y = element_text(family = "outfit")
  )

@@

#
#
#
#
#
#
#
#
#
#
#
#

>>>>

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Analysis"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
    fig-width: 12
---

@@

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)

@@

Comparing outcomes between left and right hemisphere location overall. There does not appear to be a big difference.

@@

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

@@

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs90))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 90 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

mrsCounts <- d |>
  filter(!is.na(mrs180)) |>
  group_by(ichLaterality, mrs180) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs180))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 180 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

mrsCounts <- d |>
  filter(!is.na(mrs365)) |>
  group_by(ichLaterality, mrs365) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

theme_set(theme_minimal(base_size = 20, base_family = "Figtree"))

ggplot(
  data = mrsCounts,
  aes(x = ichLaterality, y = percentPatients, fill = forcats::fct_rev(mrs365))
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  scale_fill_manual(values = myColors, breaks = c(0, 1, 2, 3, 4, 5, 6)) +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "modified Rankin score at 365 days"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )

@@

#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
